---
title: "Cohort: Weekly Progress Report"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: bootstrap
params:
  date_update: 
    value: !r Sys.Date()
    input: date
  latest_data:
    value: weekly_data.rds
    input: file
---

<!-- This has been edited for illustrative purposes - note this is not real data-->
```{css, echo=F}
.navbar {
  background-color: #668aae;
  border-color:white;
}

.navbar-inverse .navbar-brand {
  color: white!important;
}

.navbar-inverse .navbar-nav > li > a {
  color: white!important;
}

.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  color: white;
  background-color: #00366c;
}

.navbar-inverse .navbar-nav > .disabled > a,
.navbar-inverse .navbar-nav > .disabled > a:hover,
.navbar-inverse .navbar-nav > .disabled > a:focus {
  color: white;
  background-color: transparent;
}

.navbar-inverse .navbar-toggle {
  border-color: #00366c;
}

.navbar-inverse .navbar-toggle:hover,
.navbar-inverse .navbar-toggle:focus {
  background-color: #00366c;
}

.navbar-inverse .navbar-toggle .icon-bar {
  background-color: white!important;
}
```


```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(flexdashboard)
library(readxl)
library(kableExtra)
library(DT)
library(lubridate)
library(janitor)
library(RColorBrewer)
library(ggpubr)
library(epiR)
library(patchwork)
library(gtsummary)
library(gt)
library(plotly)
library(leaflet)
library(leaflet.minicharts)
library(ggmap)
library(scatterpie)
```

```{r load data}
# Load the fake data
cohort_data <- readRDS(params$latest_data)

# for the code sample I generated fake datasets, load them below
rdt_data <- readRDS(here("code_sample/data/", "RDT_data.rds"))
fever_data <- readRDS(here("code_sample/data/", "fever_data.rds"))
anemia_data <- readRDS(here("code_sample/data/", "anemia_data.rds"))
coords <- readRDS(here("code_sample/data", "coords.rds"))
schedule <- read_xlsx(here::here("code_sample/data", "visit_schedule.xlsx"))

# Load the pre-made map for plotting spatiotemporal positivity rates
load(here::here("code_sample/data", "map.rda"))
```
<p style="font-size:9pt; font-style:italic"> *Last updated: `r params$date_update` FOR ILLUSTRATIVE PURPOSES - CODE SAMPLE*</p>

```{r color palettes}
village_pal_four <- c("Bulal" = "dodgerblue3", 
                      "Megiar" = "mediumpurple3",
                      "Mirap" = "goldenrod3", 
                      "Wasab" = "palevioletred3")
village_pal <- c("Bulal" = "dodgerblue3", 
                 "Megiar-A" = "mediumpurple2", 
                 "Megiar-B" = "mediumpurple4",
                 "Mirap" = "goldenrod3", 
                 "Wasab-A" = "palevioletred2",
                 "Wasab-B" = "palevioletred4")

enrol_pal <- c("Bulal1" = "dodgerblue2", 
               "Bulal2" = "dodgerblue3", 
               "Megiar1" = "mediumpurple1",
               "Megiar2" = "mediumpurple2",
               "Megiar3" = "mediumpurple3",
               "Megiar4" = "mediumpurple4",
               "Mirap1" = "goldenrod2", 
               "Mirap2" = "goldenrod3",  
               "Wasab1" = "palevioletred1",
               "Wasab2" = "palevioletred2",
               "Wasab3" = "palevioletred3",
               "Wasab4" = "palevioletred4")
```

Follow-Up{data-orientation=rows}
=====================
```{r enrolment numbers}
tot_enrolment_numbers <- cohort_data %>% 
  filter(redcap_event_name == "enrollment_arm_1") %>% 
  tabyl(village_covid)

wasabA_tot_enrol <- tot_enrolment_numbers %>% filter(village_covid == "Wasab-A") %>% select(n) %>% as.integer()
wasabB_tot_enrol <- tot_enrolment_numbers %>% filter(village_covid == "Wasab-B") %>% select(n) %>% as.integer()
wasab_tot_enrol <- wasabA_tot_enrol + wasabB_tot_enrol

megiarA_tot_enrol <- tot_enrolment_numbers %>% filter(village_covid == "Megiar-A") %>% select(n) %>% as.integer()
megiarB_tot_enrol <- tot_enrolment_numbers %>% filter(village_covid == "Megiar-B") %>% select(n) %>% as.integer()
megiar_tot_enrol <- megiarA_tot_enrol + megiarB_tot_enrol

bulal_tot_enrol <- tot_enrolment_numbers %>% filter(village_covid == "Bulal") %>% select(n) %>% as.integer()
mirap_tot_enrol <- tot_enrolment_numbers %>% filter(village_covid == "Mirap") %>% select(n) %>% as.integer()

tot_enrol <- wasab_tot_enrol + megiar_tot_enrol + bulal_tot_enrol + mirap_tot_enrol

enrol_grp_numbers <- cohort_data %>% 
  filter(redcap_event_name == "enrollment_arm_1") %>% 
  tabyl(enrollment_group) %>% 
  rename("total_enrolled" = "n")
```

```{r followup-data-curation}
first_date_of_week <- function(year, week){
  strptime(paste(year, week, 1), format = "%Y %W %u")}

# This is the the entire breakdown of follow-up rates for each enrollment group and each follow-up visit - note that this includes the enrollment time point
followup_rate_withenrol <- cohort_data %>%
  group_by(visit, enrollment_group, epi_week, village_covid) %>%
  tally() %>%
  mutate(week_date = as.Date(first_date_of_week(2020, epi_week))) %>% 
  group_by(visit, enrollment_group) %>% 
  mutate(cum_n = cumsum(n)) %>% 
  ungroup() %>% 
  left_join(enrol_grp_numbers %>% select(enrollment_group, total_enrolled), by = "enrollment_group") %>% 
  mutate(prop_followup = n/total_enrolled) %>% 
  mutate(cumprop_followup = cum_n/total_enrolled) %>% 
  mutate(village = case_when(grepl("Bulal", enrollment_group) ~ "Bulal",
                             grepl("Megiar", enrollment_group) ~ "Megiar",
                             grepl("Mirap", enrollment_group) ~  "Mirap",
                             grepl("Wasab", enrollment_group) ~ "Wasab")) 

# This is the entire breakdown of follow-up rates for each enrollment group and each follow-up visit (i.e. this gives the entire breakdown by visit week and visit type)
followup_rate <- cohort_data %>%
  filter(redcap_event_name != "enrollment_arm_1") %>%
  group_by(visit, enrollment_group, epi_week, village_covid) %>%
  tally() %>%
  mutate(week_date = as.Date(first_date_of_week(2020, epi_week))) %>% 
  group_by(visit, enrollment_group) %>% 
  mutate(cum_n = cumsum(n)) %>% 
  ungroup() %>% 
  left_join(enrol_grp_numbers %>% select(enrollment_group, total_enrolled), by = "enrollment_group") %>% 
  mutate(prop_followup = n/total_enrolled) %>% 
  mutate(cumprop_followup = cum_n/total_enrolled) %>% 
  mutate(village = case_when(grepl("Bulal", enrollment_group) ~ "Bulal",
                             grepl("Megiar", enrollment_group) ~ "Megiar",
                             grepl("Mirap", enrollment_group) ~  "Mirap",
                             grepl("Wasab", enrollment_group) ~ "Wasab")) 

# This is the summary of follow-up rates for each enrollment group and each follow-up visit 
followup_rate_summary <- followup_rate %>% 
  group_by(visit, enrollment_group, village) %>% 
  top_n(n = 1, cumprop_followup) %>% 
  ungroup() %>% 
  select(enrollment_group, visit, cum_n, total_enrolled, cumprop_followup) %>% 
  mutate(cumprop_followup = ceiling(cumprop_followup*100)) %>% 
  arrange(enrollment_group) 

median_followup_rate <- followup_rate_summary %>% 
  group_by(enrollment_group) %>% 
  summarise(med_rate = median(ceiling(cumprop_followup)))

median_followup_rate_indiv <- cohort_data %>% 
  filter(visit != "enrollment") %>% 
  tabyl(subjid, visit) %>% adorn_totals("col") %>% 
  left_join(cohort_data %>% select(subjid, enrollment_group, village), by = "subjid") %>% 
  distinct(subjid, Total, enrollment_group, village) %>% 
  group_by(enrollment_group) %>% 
  mutate(prop_visits = round(Total/max(Total)*100, 0)) %>% 
  distinct(subjid, enrollment_group, village, prop_visits) %>% 
  summarise(med_rate = median(prop_visits)) 

# median_followup_rate_indiv %>%
#   kable(col.names = c("Enrollment group", "Median follow-up rate")) %>%
#   kable_styling(full_width = F, bootstrap_options = "striped")
  
  
subjid_fup <- cohort_data %>% filter(visit != "enrollment") %>% distinct(subjid)%>% pull(subjid)

subjid_en <- cohort_data %>% filter(visit== "enrollment") %>% pull(subjid)

subjid_LTF <- setdiff(subjid_en, subjid_fup)
```

```{r LTF}
tot_followed <- cohort_data %>% filter(visit != "enrollment") %>% distinct(subjid) %>% nrow()
LTF <- tot_enrol-tot_followed
```

```{r med-followup-groups}
bul1_rate <- median_followup_rate %>% filter(enrollment_group == "Bulal1") %>% pull(med_rate)
bul2_rate <- median_followup_rate %>% filter(enrollment_group == "Bulal2") %>% pull(med_rate)

meg1_rate <- median_followup_rate %>% filter(enrollment_group == "Megiar1") %>% pull(med_rate)
meg2_rate <- median_followup_rate %>% filter(enrollment_group == "Megiar2") %>% pull(med_rate)
meg3_rate <- median_followup_rate %>% filter(enrollment_group == "Megiar3") %>% pull(med_rate)
meg4_rate <- median_followup_rate %>% filter(enrollment_group == "Megiar4") %>% pull(med_rate)

mir1_rate <- median_followup_rate %>% filter(enrollment_group == "Mirap1") %>% pull(med_rate)
mir2_rate <- median_followup_rate %>% filter(enrollment_group == "Mirap2") %>% pull(med_rate)

was1_rate <- median_followup_rate %>% filter(enrollment_group == "Wasab1") %>% pull(med_rate)
was2_rate <- median_followup_rate %>% filter(enrollment_group == "Wasab2") %>% pull(med_rate)
was3_rate <- median_followup_rate %>% filter(enrollment_group == "Wasab3") %>% pull(med_rate)
was4_rate <- median_followup_rate %>% filter(enrollment_group == "Wasab4") %>% pull(med_rate)
```

```{r follow-up schedule}
schedule <- schedule %>% mutate(interval = interval(start_date, end_date)) 
schedule <- schedule %>% mutate(current_visit = c(as.Date(params$date_update) %within% interval))
```

Row {data-height=20}
-----------------------------------------------------------------------
### This week the field teams are visiting: **`r schedule %>% filter(current_visit == TRUE) %>% select(villages) %>% as.character()`** 

Row {data-height=180}
--------------------------------------------------------------------------------
### Follow-up diagnostic
```{r bul1-diag}
valueBox(
  value = paste0(bul1_rate, "%"),
  caption = "median follow-up rate in Bulal1",
  color = ifelse(bul1_rate >=80, "#00b200",
                 ifelse(bul1_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)

#pluck(median_followup_rate, 2, 1)
```

### Follow-up diagnostic
```{r bul2-diag}
valueBox(
  value = paste0(bul2_rate, "%"),
  caption = "median follow-up rate in Bulal2",
  color = ifelse(bul2_rate >=80, "#00b200",
                 ifelse(bul2_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

### Follow-up diagnostic
```{r meg1-diag}
valueBox(
  value = paste0(meg1_rate, "%"),
  caption = "median follow-up rate in Megiar1",
  color = ifelse(meg1_rate >=80, "#00b200",
                 ifelse(meg1_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

### Follow-up diagnostic
```{r meg2-diag}
valueBox(
  value = paste0(meg2_rate, "%"),
  caption = "median follow-up rate in Megiar2",
  color = ifelse(meg2_rate >=80, "#00b200",
                 ifelse(meg2_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

### Follow-up diagnostic
```{r meg3-diag}
valueBox(
  value = paste0(meg3_rate, "%"),
  caption = "median follow-up rate in Megiar3",
  color = ifelse(meg3_rate >=80, "#00b200",
                 ifelse(meg3_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

### Follow-up diagnostic
```{r meg4-diag}
valueBox(
  value = paste0(meg4_rate, "%"),
  caption = "median follow-up rate in Megiar4",
  color = ifelse(meg4_rate >=80, "#00b200",
                 ifelse(meg4_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

Row{data-width=50%}
--------------------------------------------------------------------------------
### Follow-up diagnostic
```{r mir1-diag}
valueBox(
  value = paste0(mir1_rate, "%"),
  caption = "median follow-up rate in Mirap1",
  color = ifelse(mir1_rate >=80, "#00b200",
                 ifelse(mir1_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

### Follow-up diagnostic
```{r mir2-diag}
valueBox(
  value = paste0(mir2_rate,"%"),
  caption = "median follow-up rate in Mirap2",
  color = ifelse(mir2_rate >=80, "#00b200",
                 ifelse(mir2_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

### Follow-up diagnostic
```{r was1-diag}
valueBox(
  value = paste0(was1_rate, "%"),
  caption = "median follow-up rate in Wasab1",
  color = ifelse(was1_rate >=80, "#00b200",
                 ifelse(was1_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

### Follow-up diagnostic
```{r was2-diag}
valueBox(
  value = paste0(was2_rate, "%"),
  caption = "median follow-up rate in Wasab2",
  color = ifelse(was2_rate >=80, "#00b200",
                 ifelse(was2_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

### Follow-up diagnostic
```{r was3-diag}
valueBox(
  value = paste0(was3_rate, "%"),
  caption = "median follow-up rate in Wasab3",
  color = ifelse(was3_rate >=80, "#00b200",
                 ifelse(was3_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

### Follow-up diagnostic
```{r was4-diag}
valueBox(
  value = paste0(was4_rate, "%"),
  caption = "median follow-up rate in Wasab4",
  color = ifelse(was4_rate >=80, "#00b200",
                 ifelse(was4_rate <=60, "#ff7f7f",
                        "#ffb54d")) 
)
```

Column{data-width=30%}
--------------------------------------------------------------------------------

### Follow-up rate summary by visit
```{r}
bul1_rows <- which(followup_rate_summary$enrollment_group == "Bulal1")
bul2_rows <- which(followup_rate_summary$enrollment_group == "Bulal2")

meg1_rows <- which(followup_rate_summary$enrollment_group == "Megiar1")
meg2_rows <- which(followup_rate_summary$enrollment_group == "Megiar2")
meg3_rows <- which(followup_rate_summary$enrollment_group == "Megiar3")
meg4_rows <- which(followup_rate_summary$enrollment_group == "Megiar4")

mir1_rows <- which(followup_rate_summary$enrollment_group == "Mirap1")
mir2_rows <- which(followup_rate_summary$enrollment_group == "Mirap2")

was1_rows <- which(followup_rate_summary$enrollment_group == "Wasab1")
was2_rows <- which(followup_rate_summary$enrollment_group == "Wasab2")
was3_rows <- which(followup_rate_summary$enrollment_group == "Wasab3")
was4_rows <- which(followup_rate_summary$enrollment_group == "Wasab4")
```

```{r}
followup_rate_summary %>% 
  mutate(cumprop_followup = cell_spec(cumprop_followup, 
                                      color = ifelse(cumprop_followup >= 80, "#00b200",
                                                     ifelse(cumprop_followup <=60, "#ff7f7f",
                                                            "#ffb54d")))) %>%
  kable(escape = F,
        col.names = c("Enrollment group", "Visit", "Participants surveyed", "Total enrolled", "Follow-up rate (%)"), 
        align = "c") %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  pack_rows("Bulal1", min(bul1_rows), max(bul1_rows)) %>% 
  pack_rows("Bulal2", min(bul2_rows), max(bul2_rows)) %>% 
  pack_rows("Megiar1", min(meg1_rows), max(meg1_rows)) %>% 
  pack_rows("Megiar2", min(meg2_rows), max(meg2_rows)) %>% 
  pack_rows("Megiar3", min(meg3_rows), max(meg3_rows)) %>% 
  pack_rows("Megiar4", min(meg4_rows), max(meg4_rows)) %>% 
  pack_rows("Mirap1", min(mir1_rows), max(mir1_rows)) %>% 
  pack_rows("Mirap2", min(mir2_rows), max(mir2_rows)) %>% 
  pack_rows("Wasab1", min(was1_rows), max(was1_rows)) %>% 
  pack_rows("Wasab2", min(was2_rows), max(was2_rows)) %>% 
  pack_rows("Wasab3", min(was3_rows), max(was3_rows)) %>% 
  pack_rows("Wasab4", min(was4_rows), max(was4_rows))
```

### Median participant follow-up rate
```{r, out.width="50%"}
diagnostic_pal <- c(">79" = "#00b200", "61-79" = "#ffb54d", "<61" = "#ff7f7f")

median_followup_rate_indiv %>% 
  filter(!is.na(enrollment_group)) %>%
  mutate(color = case_when(med_rate >= 80 ~ ">79",
                           med_rate <=60 ~ "<61",
                           TRUE ~ "61-79")) %>%
  ggplot(aes(x = enrollment_group, y = med_rate, fill = color)) +
    geom_bar(stat = "identity") +
    geom_hline(yintercept = 80, linetype = "dashed", color = "black") +
    geom_hline(yintercept = 60, linetype = "dashed", color = "black") +
    #geom_pointrange(aes(ymin = 0, ymax = med_rate, color = color)) + 
    geom_text(aes(label = paste0(med_rate, "%"), color = color), vjust = -0.5, size = 4) +
    scale_fill_manual(values = diagnostic_pal,
                      name = "") +
    scale_color_manual(values = diagnostic_pal) +
    labs(x = "enrollment group",
         y = "median participant follow-up rate (%)") +
    theme_light() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1))
```


### Potential loss to follow-up (n=`r LTF`)
```{r, out.width="50%"}
cohort_data %>% 
  filter(subjid %in% subjid_LTF) %>% 
  count(subjid, enrollment_group) %>% 
  ggplot(aes(x = enrollment_group, y = n, fill = enrollment_group)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = enrol_pal,
                      name = "") +
    labs(x = "enrollment group",
         y = "number of participants potentially lost to follow-up") +
    theme_light() 
```

<!-- ### Potential loss to follow-up participant info{data-height=50%} -->
<!-- ```{r} -->
<!-- cohort_data %>%  -->
<!--   filter(subjid %in% subjid_LTF) %>%  -->
<!--   select(subjid, bl_hhid, bl_sex, bl_agey, enrollment_group) %>%  -->
<!--   mutate_if(is.character, as.factor) %>%  -->
<!--   rename("Participant ID" = "subjid", -->
<!--          "Household ID" = "bl_hhid", -->
<!--          "Sex" = "bl_sex", -->
<!--          "Age (years)" = "bl_agey", -->
<!--          "Enrollment group" = "enrollment_group") %>%  -->
<!--   datatable(extensions = "Buttons",  -->
<!--             options = list(dom = "Bfrtip",  -->
<!--                            buttons = (list( -->
<!--                              "copy", list( -->
<!--                                extend = "collection",  -->
<!--                                buttons = c("csv", "excel"),  -->
<!--                                text = "Download")))),  -->
<!--             rownames = F,  -->
<!--             filter = "top", -->
<!--             style = "bootstrap",  -->
<!--             height = "50px", -->
<!--             width = "50px") -->
<!-- ``` -->


Monthly trends{style="position:relative;"}
=====================

Column{style="height:50pc;width:50pc"}
--------------------------------------------------------------------------------

### Febrile illness{.no-padding}
```{r, fig.fullwidth=TRUE}
ggplotly(fever_data %>% 
  ggplot(aes(x = as.Date(visit_month), y = prop, color = village, group = village)) +
    geom_point() +
    geom_line() +
    scale_color_manual(values = village_pal_four) +
    scale_y_continuous(labels = scales::percent,
                       limits = c(0, 1)) +
    scale_x_date(date_breaks = "month",
                 date_labels = "%b-%Y") +
    labs(x = "month",
         y = "Prevalence of fever ≥37.5ºC") + 
    theme_light() +
    theme(axis.text.x = element_text(angle = 30, hjust = 1)))
```

### RDT positivity{.no-padding}
```{r, fig.fullwidth=TRUE}
ggplotly(rdt_data %>% 
  ggplot(aes(x = as.Date(visit_month), y = prop, color = village, group = village)) +
    geom_point() +
    geom_line() +
    scale_color_manual(values = village_pal_four) +
    scale_y_continuous(labels = scales::percent,
                       limits = c(0,1)) +
    scale_x_date(date_breaks = "month",
                 date_labels = "%b-%Y") +
    labs(x = "month",
         y = "RDT positivity",
         caption = expression(italic("Note: an RDT is only performed if participant is unwell and/or has a fever"))) + 
    theme_light() +
    theme(axis.text.x = element_text(angle = 30, hjust = 1)))
```

Column{style="height:50pc;width:50pc"}
--------------------------------------------------------------------------------

### Spatiotemporal RDT positivity{.no-padding}
```{r}
rdt_prop_spatiotemp <- cohort_data %>% tabyl(village, rdt_result, visit_month) %>% adorn_totals("col")

rdt_prop_spatiotemp <- map2_df(rdt_prop_spatiotemp, names(rdt_prop_spatiotemp), ~ mutate(.x, visit_month = .y)) 

rdt_prop_spatiotemp <- rdt_prop_spatiotemp %>% mutate(radius = (0.4 * sqrt(Total) / sqrt(max(Total)))) 

rdt_prop_spatiotemp <- rdt_prop_spatiotemp %>% left_join(coords, by = "village")

# remove the 0's
rdt_prop_spatiotemp <- rdt_prop_spatiotemp %>% filter(Total > 0)

rdt_prop_spatiotemp <- rdt_prop_spatiotemp %>% mutate(month = paste0(month(visit_month, label = T), "-", year(visit_month)))

rdt_prop_spatiotemp <- rdt_prop_spatiotemp %>% mutate(Positive = `Positive (Pf or Mixed)` + `Positive (Pf Single)` + `Positive (Pv, Po, Pm)`)

# New labels for month variable
rdt_prop_spatiotemp <- rdt_prop_spatiotemp %>% mutate(visit_month = factor(visit_month, levels = .$visit_month, labels = rdt_prop_spatiotemp$month))
```

```{r, fig.fullwidth=TRUE}
ggmap(map) +
  geom_scatterpie(data = rdt_prop_spatiotemp, 
                  aes(x = med_lon, 
                      y = med_lat, 
                      r = radius/12,
                      group = village),
                  cols = c("Negative", "Positive")) +
  scale_fill_manual(values = c("grey", "#ff678d"),
                    name = "RDT result") +
  # geom_scatterpie_legend(rdt_prop_spatiotemp$radius/10,
  #                        n = 2,
  #                        labeller = function(x) x = unique(rdt_prop_spatiotemp$Total),
  #                        x = -145.63,
  #                        y = -4.92) +
  labs(x = "longitude",
       y = "latitude") +
  theme_bw() +
  facet_wrap(~visit_month) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Anemia{.no-padding}
```{r, fig.fullwidth=TRUE}
anemia_data %>% 
  ggplot(aes(x = reorder(month, visit_month), y = hb, fill = sex)) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 11, linetype = "dashed", color = "black") +
  scale_fill_brewer(palette = "Paired", 
                    labels = c("Female", "Male"),
                    name = "") +
  scale_y_continuous(breaks = scales::pretty_breaks(n=10), limits = c(0, 20)) +
  labs(x = "month",
       y = "hemoglobin (g/dL)",
       caption = expression(italic("Note: dashed line indicates mild anemia threshold (<11g/dL)"))) + 
  facet_wrap(village~.) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```
